Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-21 paper/paper.tex
adding datarepo

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~This paper contributes the following: 1)~A
comprehensive study to analyze the effectiveness of diversity-aware
techniques to find functional bugs in popular \javascript\ engines.
2)~A number of bugs found and fixed. We reported a total of
\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
for diversity-aware testing. We made our testing infrastructure,
results, and experimental scripts available to the public. (upon
request for anonymity.)

@@

@@

This section discusses a selection of bugs reports. The selection
criteria we used was: (i) to cover each engine that we found
bugs--\chakra, \jsc, and \veight, (ii) to cover a different
technique--test transplantation and differential testing (with
\radamsa\ and with \quickfuzz), (iii) to cover a case of rejected bug
report, and (iv) to use short test inputs (for space).

@@

The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
ascii}. The unary plus expression ``\CodeIn{+a}", used in the
assertion, is equivalent to the operation
\CodeIn{To Number(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)~\cite{unary-plus}. This test fails in all engines but
\chakra{}. For all three engines the string cannot be parsed as an
hexadecimal. As such, they produce a NaN as result and the test fails
as expected. \chakra{}, in contrast, incorrectly converts the string
to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

@@

In the near future, we plan to explore techniques to prioritize the
warnings reported by these techniques and to continue involving
students in the task of diagnosing these warnings. Using learning
techniques for prioritization, similar to what Chen and
colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
seems a promising starting point for this improvement. The result
data, infrastructure, and experimental scripts we prepared to run this
study will be available upon request.

>>>>

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~This paper contributes the following: 1)~A
comprehensive study to analyze the effectiveness of diversity-aware
techniques to find functional bugs in popular \javascript\ engines.
2)~A number of bugs found and fixed. We reported a total of
\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
for diversity-aware testing. The scripts to run the experiments will
be available upon request. The data is publicly available \dataRepo{}.

@@

\noindent
\textbf{Data Availability.}~The data, including the tests, warning
reports, and diagnostic outcomes, is publicly available from a
preserved repository \dataRepo.

@@

This section discusses a sample of bugs reports. The selection
criteria we used was: (i) to cover all engines we found bugs--\chakra,
\jsc, and \veight, (ii) to cover each technique--test transplantation
and differential testing (with \radamsa\ and with \quickfuzz), (iii)
to cover a case of rejected bug report, and (iv) to use short tests
(for space).

@@

The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
ascii}. The unary plus expression ``\CodeIn{+a}", used in the
assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)~\cite{unary-plus}. This test fails in all engines but
\chakra{}. For all three engines the string cannot be parsed as an
hexadecimal. As such, they produce a NaN as result and the test fails
as expected. \chakra{}, instead, incorrectly converts the string
to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

@@

In the near future, we plan to explore techniques to prioritize the
warnings reported by these techniques and to continue involving
students in the task of diagnosing these warnings. Using learning
techniques for prioritization, similar to what Chen and
colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
seems a promising starting point for this improvement.

The scripts to run the experiments for this study will be available
upon request. The data is publicly available \dataRepo{}.
